### 2022-07-06 tex/sample_paper.tex
updates

\usepackage{aistats2021}
\usepackage{cite}

@@

\subsection{Simplex Transforms}

\subsubsection{Softmax Transform}
The softmax function can be understood from Multinomial Logistic Regression employed for predicting probabilities of a Categorically distributed variable. Geometrically it maps $R^K$ to the boundary of a unit K-simplex(it is simply the convex hull of $k+1$ affinely independent points in $R^K$. Essentially it transforms a vector of size K to another vector of size K where the outputs sum to 1. It is worth noting that the mapping is actually from $R^K$ to $R^{K-1}$, so when a vector of size $K$ is transformed the $K_th$ vector is simply $1$- sumofk-1 vectors

>>>>

\usepackage{aistats2021}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}

@@

\subsection{Simplex}

A simplex is a set of non negative vectors that sum up to a constant $a$, this can be written as:
\begin{equation*}
\Delta=\left\{\mathbf{x} \in \mathbb{R}^{n} \mid\left\langle\mathbf{x}, \mathbf{1}_{n}\right\rangle=a, \mathbf{x} \geq 0\right\}
\end{equation*}

In computational works, we generally care about the unit simplex, this is the special case where $ a = 1$. Geometrically, an \textit{n-simplex} is the convex closure of $n+1$ affinely independent set of points $x_0, x_1, \dots x_n$. It is the simplest polytope for $n$-dimensions(in this case we will be looking at a simplex as a convex polytope instead of abstract). An $n-simplex$ can be represented in the barycentric coordinate system with weighted vertices, as follows:
\begin{equation*}
\Delta = \left\{x_{0} u_{0}+\cdots+x_{n} u_{n} \mid \sum_{i=0}^{n} x_{i}=1\\
 \text{ and } x_{i} \geq 0 \text { for } i=0, \ldots, k\right\}
\end{equation*}

With this representation, taking $u_{i}=1$, the $n$ unit simplex can be written as: 
\begin{equation*}
\left\{x \in \mathbb{R}^{n}: x_{0}+\cdots+x_{n-1}=1, x_{i} \geq 0 \text { for } i=0, \ldots, k-1\right\}
\end{equation*}

A \textit{unit simplex} on $R^n$ is an $n - 1$ dimensional simplex with unit vectors as vertices. Notice the unit weights, this set only has $n-1$ affinely independent points.

Sum to one constraints are useful in probabilistic inference, often used for modeling categorical responses. The rest of the section describes various transforms used to map a simplex to an unconstrained space ($R^n$).
\subsubsection{Softmax Transform}
The softmax function can be understood from Multinomial Logistic Regression employed for predicting probabilities of a Categorically distributed variable. Geometrically it maps $R^K$ to the boundary of a unit K-simplex(it is simply the convex hull of $k+1$ affinely independent points in $R^K$. Essentially it transforms a vector of size K to another vector of size K where the outputs sum to 1. It is worth noting that the mapping is actually from $R^K$ to $R^{K-1}$, so when a vector of size $K$ is transformed the $K_th$ vector is simply $1$- sumof k-1 vectors
